---
title: "p8105_hw2_st3431"
output: github_document
date: "2022-10-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readxl)
```

##Problem 1 

```{r}
subway_df=read_csv("hw2_data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv") %>% 
  janitor::clean_names() %>%
  select(ada, vending, line:entry) %>%
   mutate(entry=recode(entry, `YES` = 'true', `NO` = 'false'), 
         entry=factor(entry))

```

This data is not necessarily tidy because we need to convert the route variable to a long format which will help focus on specific routes. 

```{r}
subway_df %>% 
  select(station_name, line) %>% 
  distinct

subway_df %>% 
   filter(ada == TRUE) %>% 
  select(station_name, line) %>% 
  distinct

subway_df %>% 
  filter(vending == "NO") %>% 
  pull(entry) %>% 
  mean
```

```{r}
```

## Problem 2 

Cleaning The Mr. Trash Sheet

```{r}
mrtrash_df=
  read_excel("hw2_data/Trash Wheel Collection Data.xlsx", sheet="Mr. Trash Wheel") %>% 
  janitor::clean_names() %>% 
  drop_na(dumpster) %>% 
  mutate(sports_balls, as.integer(round(sports_balls))) %>% 
  mutate(across(.col= (c("year")), as.integer)) %>% 
  mutate(mrtrash= "mr")
```

```{r}
professortrash_df=
  read_excel("hw2_data/Trash Wheel Collection Data.xlsx", sheet="Professor Trash Wheel") %>% 
  janitor::clean_names() %>% 
  drop_na(dumpster) %>% 
  mutate(across(.col= (c("year")), as.integer)) %>% 
  mutate(proftrash= "professor")
```

Combining the data sets 

```{r}
trash_combined= 
  bind_rows(mrtrash_df, professortrash_df) %>% 
  janitor::clean_names() 
 
  
sum(professortrash_df$weight_tons)

filter(mrtrash_df, year == 2020) %>% 
  summarise(sum(sports_balls))
```

This data has some key variables such as the different types of trash that are found, including things like grocery bags, chip bags and other kinds of trash. The total weight of the trash in the professor trash wheel data set is 135.5 tons and the number of sports balls found in 2020 in the mr. trash wheel was 856.





